### 2015-05-14 paper.tex
Both algs added now

We provide the algorithm in fig (TODO), and give a very high level overview of the two main "stages" included.

@@

>>>>

We provide the algorithm in Alg. \ref{alg:cluster}, and give a very high level overview of the two main "stages" included.

@@

\begin{algorithm}
\caption{k-Mean Clustering in the General Case}\label{alg:cluster2}
\begin{algorithmic}[1]
\Procedure{Cluster}{}
\BState \textbf{Input:} $w, \delta \leq 1, \alpha > 0, k.$
\BState \textbf{Step 1:} Construct the $\tau$-threshold graph $G_{\tau}$ with $\tau = 2d_{crit} = \frac{\alpha w}{5 \delta}$.

\BState \textbf{Step 2:} For $j = 1$ to $k$ do:
\State Pick the vertex $v_j$ of the highest degree in $G_{\tau}$.
\State Remove $v_j$ and its neighborhood from $G_{\tau}$ and call this cluster $C(v_j)$.
\BState \textbf{Step 3:} Output the $k$ clusters $C(v_1), ..., C(v_{k-1}), S - \bigcup_{i=1}^{k-1}C(v_i)$.

\EndProcedure
\end{algorithmic}
\end{algorithm}
